---
title: "PSC-012Y Unit 1: Foundations in R, Quarto, and Tidy Data"
format:
  html:
    embed-resources: true
---

## Syllabus Alignment

- **Lecture date:** April 3, 2026
- **Tutorial date:** April 6, 2026
- **Lab date:** April 8, 2026
- **Statistical concept:** Units of observation, variables, research questions, tidy data
- **Programming concept:** `read_csv()`, `glimpse()`, `select()`, `filter()`, first `ggplot()`

## Goals

- Open a project in RStudio.
- Render a Quarto document.
- Read a CSV from the local `data/` folder.
- Identify rows, columns, and variable types.

## Local Data Check

```{r}
unit1_data <- read.csv("data/student_checkins.csv", stringsAsFactors = FALSE)
unit1_data
table(unit1_data$attendance)
summary(unit1_data$hours_studied)
```

## Tidyverse Starter

```{r}
#| eval: false
library(readr)
library(dplyr)
library(ggplot2)

student_checkins <- read_csv("data/student_checkins.csv")

student_checkins |>
  filter(attendance == "Present") |>
  select(student_id, section, preferred_topic)

student_checkins |>
  ggplot(aes(x = preferred_topic)) +
  geom_bar()
```

## Notes

Use this file as the starting point for lecture examples, tutorial notes, or the first lab activity.
