---
title: "PSC-012Y Unit 6: Relationships Between Continuous Variables"
format:
  html:
    embed-resources: true
---

## Syllabus Alignment

- **Lecture date:** May 15, 2026
- **Tutorial date:** May 18, 2026
- **Lab date:** May 20, 2026
- **Statistical concept:** Association, trend, correlation, regression as line-of-best-fit intuition
- **Programming concept:** Scatterplots, `geom_smooth(method = "lm")`, `cor()`, simple `lm()` output reading

## Goals

- Visualize the relationship between two continuous variables.
- Interpret correlation direction and strength.
- Use a simple linear model as a descriptive tool.

## Local Data Check

```{r}
unit6_data <- read.csv("data/screen_time_and_focus.csv")
cor(unit6_data$screen_time_hours, unit6_data$assignment_grade)
summary(lm(assignment_grade ~ screen_time_hours, data = unit6_data))
```

## Tidyverse Starter

```{r}
#| eval: false
library(readr)
library(ggplot2)

focus_data <- read_csv("data/screen_time_and_focus.csv")

focus_data |>
  ggplot(aes(x = screen_time_hours, y = assignment_grade)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

## Notes

Use this notebook to draft scatterplots, correlation write-ups, and introductory regression interpretation.
