---
title: "PSC-012Y Unit 3: Categorical Data and Bar Charts"
format:
  html:
    embed-resources: true
---

## Syllabus Alignment

- **Lecture date:** April 17, 2026
- **Tutorial date:** April 20, 2026
- **Lab date:** April 22, 2026
- **Statistical concept:** Counts, proportions, observed vs expected counts, introductory association testing
- **Programming concept:** `count()`, grouped summaries, `geom_bar()`, `chisq.test()`

## Goals

- Summarize categorical variables with counts and proportions.
- Create a simple bar chart.
- Introduce the logic of a chi-square test.

## Local Data Check

```{r}
unit3_data <- read.csv("data/campus_club_poll.csv", stringsAsFactors = FALSE)
table(unit3_data$club_type)
table(unit3_data$club_type, unit3_data$attended_event)
chisq.test(table(unit3_data$club_type, unit3_data$attended_event))
```

## Tidyverse Starter

```{r}
#| eval: false
library(readr)
library(dplyr)
library(ggplot2)

club_poll <- read_csv("data/campus_club_poll.csv")

club_poll |>
  count(club_type, attended_event)

club_poll |>
  ggplot(aes(x = club_type, fill = attended_event)) +
  geom_bar(position = "dodge")
```

## Notes

This file is a good place to draft lecture examples about counts, proportions, and associations between two categorical variables.
