---
title: "PSC-012Y Unit 4: Continuous Data and Distributions"
format:
  html:
    embed-resources: true
---

## Syllabus Alignment

- **Lecture date:** May 1, 2026
- **Tutorial date:** May 4, 2026
- **Lab date:** May 6, 2026
- **Statistical concept:** Center, spread, skew, outliers
- **Programming concept:** `summarise()`, `mean()`, `median()`, `sd()`, `IQR()`, histograms, density plots, boxplots

## Goals

- Describe a distribution using center and spread.
- Compare summary measures for the same variable.
- Build toward visualizing continuous data clearly.

## Local Data Check

```{r}
unit4_data <- read.csv("data/wellbeing_scores.csv")
summary(unit4_data$sleep_hours)
sd(unit4_data$sleep_hours)
IQR(unit4_data$exercise_minutes)
```

## Tidyverse Starter

```{r}
#| eval: false
library(readr)
library(dplyr)
library(ggplot2)

wellbeing <- read_csv("data/wellbeing_scores.csv")

wellbeing |>
  summarise(
    mean_sleep = mean(sleep_hours),
    median_sleep = median(sleep_hours),
    sd_sleep = sd(sleep_hours),
    iqr_exercise = IQR(exercise_minutes)
  )

wellbeing |>
  ggplot(aes(x = sleep_hours)) +
  geom_histogram(binwidth = 0.5)
```

## Notes

Use `figures/` for exported versions of histograms, density plots, or boxplots created during the unit.
