---
title: "PSC-012Y Unit 7: Free-Response Text as Data"
format:
  html:
    embed-resources: true
---

## Syllabus Alignment

- **Lecture date:** May 22, 2026
- **Tutorial date:** May 26, 2026
- **Lab date:** May 27, 2026
- **Statistical concept:** Word frequency, stop words, sentiment, strengths and limits of word clouds
- **Programming concept:** `unnest_tokens()`, stop-word removal, `count()`, joins, word clouds, simple sentiment summaries

## Goals

- Treat text responses as analyzable data.
- Start with simple counts before moving to more advanced text workflows.
- Leave space for discussing strengths and limitations of text summaries.

## Local Data Check

```{r}
unit7_data <- read.csv("data/reflection_text.csv", stringsAsFactors = FALSE)
nchar(unit7_data$response_text)
head(unit7_data$response_text, 3)
```

## Tidytext Starter

```{r}
#| eval: false
library(readr)
library(dplyr)
library(tidytext)

reflections <- read_csv("data/reflection_text.csv")

reflections |>
  unnest_tokens(word, response_text) |>
  count(word, sort = TRUE)
```

## Notes

Use this project to draft examples about tokenization, stop-word removal, and simple sentiment or frequency summaries.
