---
title: "Unit 0 Setup"
author: 
  - name: "Your Name here" # replace this with your name + ALSO NAME THE DOCUMENT CORRECTLY!
    affiliations:
      - name: "The University of California, Davis"
date: last-modified
date-format: "dddd MMM D, YYYY [at] h:mm:ss A z"
subtitle: "PSC-012Y"
format:
  html:
    toc: true
    toc-depth: 3
    fig-align: center
    fig-width: 5
    fig-height: 5
    embed-resources: true
execute:
  echo: true
editor_options:
  chunk_output_type: console
---

## Welcome

Welcome to PSC-012Y. This short activity is here to help you get comfortable with the basic workflow we will use throughout the course.

You do not need any prior experience with `R` to complete this. The goal is simply to practice a few small steps:

- typing into a Quarto document
- running a code chunk
- rendering your work to HTML
- submitting the rendered file

This should only take about 5 to 8 minutes.

::: {.callout-tip}
If you are new to this kind of document, that is completely fine. You are not expected to know what everything means yet. For now, just follow the steps one at a time.
:::

## What To Do

Complete the five small tasks below, then render this document to HTML and submit the HTML file.

## 1. Add Your Name

Replace the placeholder text below with your name.

**Name:** Your Name Here

## 2. Add One Sentence About How You Feel Starting The Course

Replace the placeholder sentence below with one sentence in your own words.

I am feeling...

## 3. Run A Tiny Code Chunk

Click the green run arrow in the code chunk below.

```{r}
1 + 1
```

You should see output appear below the chunk after you run it.

## 4. Run One More Small Code Chunk

Run the next chunk as well. It is just here to help you get used to seeing `R` print something to the screen.

```{r}
"Hello, PSC 012Y!"
```

## 5. Answer A Short Reflection Prompt

Write one or two sentences below answering this question:

**What do you hope to learn in this class?**

Your response:

## Render And Submit

When you are finished:

1. Click `Render`.
2. Wait for the HTML file to open.
3. Make sure the rendered file includes your name, your sentence, your reflection, and the output from both code chunks.
4. Submit the rendered HTML file.

::: {.callout-note}
If your computer is having trouble with local `RStudio`, you may complete this in `Posit Cloud` instead and render the same HTML output there.
:::
