---
title: "PSC-012Y Unit 5: Uncertainty and Comparing Groups"
format:
  html:
    embed-resources: true
---

## Syllabus Alignment

- **Lecture date:** May 8, 2026
- **Tutorial date:** May 11, 2026
- **Lab date:** May 13, 2026
- **Statistical concept:** Sampling variability, confidence intervals, two-group and multi-group comparisons, p-values in plain language
- **Programming concept:** Summary tables, mean plots, error bars, `t.test()`, `aov()`

## Goals

- Compare group means.
- Introduce uncertainty in plain language.
- Use inferential tools as extensions of descriptive summaries.

## Local Data Check

```{r}
unit5_data <- read.csv("data/study_groups.csv", stringsAsFactors = FALSE)
aggregate(quiz_score ~ study_group, data = unit5_data, FUN = mean)
t.test(quiz_score ~ I(study_group == "Tutor"), data = unit5_data)
summary(aov(quiz_score ~ study_group, data = unit5_data))
```

## Tidyverse Starter

```{r}
#| eval: false
library(readr)
library(dplyr)
library(ggplot2)

study_groups <- read_csv("data/study_groups.csv")

study_groups |>
  group_by(study_group) |>
  summarise(
    mean_score = mean(quiz_score),
    sd_score = sd(quiz_score),
    n = n()
  )

study_groups |>
  ggplot(aes(x = study_group, y = quiz_score)) +
  stat_summary(fun = mean, geom = "col") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2)
```

## Notes

This project is set up for lecture examples that compare groups using both descriptive and inferential tools.
