---
title: "PSC-012Y Unit 2: Variable Types and Data Wrangling"
format:
  html:
    embed-resources: true
---

## Syllabus Alignment

- **Lecture date:** April 10, 2026
- **Tutorial date:** April 13, 2026
- **Lab date:** April 15, 2026
- **Statistical concept:** Categorical vs continuous, nominal vs ordinal, missing data
- **Programming concept:** `mutate()`, `rename()`, `arrange()`, `count()`, `forcats`

## Goals

- Practice identifying categorical and continuous variables.
- Notice where missing values appear.
- Set up a place to document cleaning decisions.

## Local Data Check

```{r}
unit2_data <- read.csv("data/messy_survey.csv", stringsAsFactors = FALSE)
unit2_data
colSums(is.na(unit2_data))
table(unit2_data$class_year)
```

## Tidyverse Starter

```{r}
#| eval: false
library(readr)
library(dplyr)
library(forcats)

survey <- read_csv("data/messy_survey.csv")

survey |>
  rename(r_comfort = comfort_r) |>
  mutate(
    first_gen = fct_infreq(first_gen),
    sleep_group = if_else(hours_sleep >= 7, "7+ hours", "under 7 hours")
  ) |>
  arrange(class_year)
```

## Notes

Use the `notes/` folder to track variable definitions, recoding decisions, or questions to bring to lab.
